How South Koreans View Democracy?

### 2024-04-18 paper/paper.qmd
Update the writing from paper

In South Korea, a nation where I was born and raised, the rapid and profound impacts of globalization have redefined the socio-economic and political landscape. As democracy inherently upholds the principle of political equality, ensuring that every citizen has a voice in the political discourse, these global forces present significant challenges. South Korea, characterized by swift economic growth and transformative political shifts, provides a critical context for exploring these challenges. These changes impact more than just the economy; they deeply influence the democratic ethos, raising crucial questions about the sustainability of political equality amidst pervasive transformations. Thus, the citizens of South Korea find themselves navigating an altered political and economic terrain, necessitating a critical reevaluation of democratic values in response to these global dynamics.

>>>>

In South Korea, a nation where I was born and raised, the rapid and profound impacts of globalization have redefined the socio-economic and political landscape. As democracy inherently upholds the principle of political equality, ensuring that every citizen has a voice in the political discourse, these global forces present significant challenges. South Korea, characterized by swift economic growth and transformative political shifts, provides a critical context for exploring these challenges. These changes impact more than just the economy; they deeply influence the democratic ethos, raising crucial questions about the sustainability of political equality amidst pervasive transformations [@article]. Thus, the citizens of South Korea find themselves navigating an altered political and economic terrain, necessitating a critical reevaluation of democratic values in response to these global dynamics.
